Effects of Weather on Maize Yield in Kenya

### 2019-01-16 presentations/January2019/presentation1.tex
presssssssee

\usepackage{amsmath}  
\usepackage{multirow,graphicx,array}
\usepackage{multicol}
\usepackage{hhline}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{threeparttable,booktabs}
\usepackage{chngcntr}
\usepackage{dcolumn}
\usepackage{caption}
\usepackage{fixltx2e}
\usepackage{rotating}
\usepackage{amssymb}

@@

@@

$y_{it}$ &$=$& Maize yield t/hectares, county $i$ in year $t$\\
$\boldsymbol{\beta}$ &$=$& Vector of effects of other covariates\\
$X_{i,t}$ &$=$& Matrix of values of other covariates in county $i$ in year $t$\\
$\epsilon_{i,t}$ &$=$& Error term \\
\end{tabular}
\end{small}
\end{table}

@@

\begin{column}{0.5\textwidth} 
\begingroup
\everymath{\Large}
\begin{align*}
\begin{array}{lcl}
 log(y_{\scriptscriptstyle it} )&=&\sum_{\scriptscriptstyle m=1}^{\scriptscriptstyle p} \beta^{\scriptscriptstyle m}x^{\scriptscriptstyle m}_{\scriptscriptstyle it}+ \sum_{\scriptscriptstyle n=1}^{\scriptscriptstyle q}b^{\scriptscriptstyle n}_{\scriptscriptstyle i}z^{\scriptscriptstyle n}_{\scriptscriptstyle it}+\epsilon_{\scriptscriptstyle it}
\end{array}
\end{align*}
\endgroup
\end{column}

\begin{column}{0.5\textwidth} 
\begingroup
\everymath{\footnotesize}
\begin{align*}
\begin{array}{ll}
i=1,...,47 & \text{counties}
\end{array}
\end{align*}
\endgroup
\end{column}
\end{columns}

$y_{it}$ &$=$& Maize yield t/hectares, county $i$ in year $t$\\
$\alpha_i$ &$=$& Fixed effects), county $i$\\
{\color{darkblue}$\delta$ }&{\color{darkblue}$=$}&{\color{darkblue}{Effect of drought on economy}}\\

$X_{i,t}$ &$=$& Matrix of values of other covariates in county $i$ in year $t$\\
$\epsilon_{i,t}$ &$=$& Error term \\
\end{tabular}
\end{small}
\end{table}

>>>>

\usepackage{amsmath}  
\usepackage{multirow,graphicx,array}
\usepackage{multicol}
\usepackage{hhline}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{threeparttable,booktabs}
\usepackage{chngcntr}
\usepackage{dcolumn}
\usepackage{caption}
\usepackage{fixltx2e}
\usepackage{rotating}
\usepackage{amssymb}
 \usepackage{setspace}

@@

\begin{frame}
\frametitle{\small Linear mixed effects models}\label{Methods}

\begin{itemize}
\item \small Slopes allowed to vary across counties
\end{itemize}

@@

\begin{table}
\begin{footnotesize}
\setstretch{1.23}
\begin{tabular}{lll}

$t$&$=$&index for year ($1981-2017$) \\
$y_{\scriptscriptstyle it}$ &$=$&maize yield tones/hectares, county $i$, year $t$\\
${\beta}^{m}$, \footnotesize{\textit{m=1,...p}}&$=$&\textit{p} fixed effects parameters\\
$x^{m}_{it}$, \footnotesize{\textit{m=1,...,p}}, \footnotesize{\textit{i=1,...,47}} &$=$&fixed effects regressors, county \textit{i}, year \textit{t}\\
$b^{n}_i$, \footnotesize{\textit{n=1,...q}}, \footnotesize{\textit{i=1,...,47}}&$=$&\textit{q} random effects parameters -\textbf{vary over county \textit{i}}\\
$z^{n}_{it}$, \footnotesize{\textit{n=1,...,q}}, \footnotesize{\textit{i=1,...,47}} &$=$&random effects regressors, county \textit{i}, year \textit{t}\\
$\epsilon_{it}$ &$=$&error term \\
\end{tabular}
\end{footnotesize}
\end{table}

@@

\begin{column}{0.6\textwidth} 
\begingroup
\everymath{\Large}
\begin{align*}
\begin{array}{lcl}
 log(y_{\scriptscriptstyle it} )&=&\sum_{\scriptscriptstyle m=1}^{\scriptscriptstyle p} \beta^{\scriptscriptstyle m}x^{\scriptscriptstyle m}_{\scriptscriptstyle it}+ \sum_{\scriptscriptstyle n=1}^{\scriptscriptstyle q}b^{\scriptscriptstyle n}_{\scriptscriptstyle i}z^{\scriptscriptstyle n}_{\scriptscriptstyle it}+\epsilon_{\scriptscriptstyle it}
\end{array}
\end{align*}
\endgroup
\end{column}

\begin{column}{0.4\textwidth} 
\begingroup
\everymath{\footnotesize}
\begin{align*}
\begin{array}{ll}
i=1,...,47 & \text{counties}
\end{array}
\end{align*}
\endgroup
\end{column}
\end{columns}

\begin{table}
\begin{footnotesize}
\setstretch{1.23}
\begin{tabular}{lll}

$t$&$=$&index for year ($1981-2017$) \\
$y_{\scriptscriptstyle it}$ &$=$&maize yield tones/hectares, county $i$, year $t$\\
${\beta}^{m}$, \footnotesize{\textit{m=1,...p}}&$=$&\textit{p} fixed effects parameters\\
$x^{m}_{it}$, \footnotesize{\textit{m=1,...,p}}, \footnotesize{\textit{i=1,...,47}} &$=$&fixed effects regressors, county \textit{i}, year \textit{t}\\
$b^{n}_i$, \footnotesize{\textit{n=1,...q}}, \footnotesize{\textit{i=1,...,47}}&$=$&\textit{q} random effects parameters -\textbf{vary over county \textit{i}}\\
$z^{n}_{it}$, \footnotesize{\textit{n=1,...,q}}, \footnotesize{\textit{i=1,...,47}} &$=$&random effects regressors, county \textit{i}, year \textit{t}\\
$\epsilon_{it}$ &$=$&error term \\
\end{tabular}
\end{footnotesize}
\end{table}
